Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
edited part a of monster lemma

\[
	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor
\]

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by a dimension count form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

\noindent
so
\[
	-\ord^{\halfcan'}_P(\prod_{j=1}^n z_j) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} < \frac{\alpha}{
\beta}$ is not a best lower approximation.  Choose a
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\end{equation}

Using this fact, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
\]
and for each $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$.
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

>>>>

\[
	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor.
\]

\noindent
So, \todo{Aaron: Presumably this is Riemann Roch, but you should explain why, as I don't see it immediately.} there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$. Hence, by a dimension count, these sections form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$. Then for each $j$, \todo{Aaron: I don't see why either of the next 2 claims hold, but maybe I'm being silly.}
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

\noindent
so
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$. \todo{This sentence on genericness seems like it does not belong in the proof.}

Choose $c,d\in \mathbb{N}$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
\beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so \todo{Why does the next equation follow from this inequality?}\todo{Aaron: Is it true that $c_1 \leq \cdots \leq c_n$? I think it is true and that it is implicitly being used here and later. Perhaps this needs to be said, or perhaps it doesn't, I'm not sure.}
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\begin{equation}\label{eqn:c-from-lower-terms}
	c_i +\left\lfloor (d-d_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
\end{equation}

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
\]
and for each $i \in \mathbb{N}$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j S_{i-j}.
\]
Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$. \todo{Perhaps it's worth reminding the reader here that $y_i$ are as in the statement of (a) and have order $-c_i$.}
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$. \todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper? I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
